### 2025-09-16 data-visualization.qmd
20250916 - update visualization to 2025

```{r}
pbp_regularSeason <- nfl_pbp %>% 
  dplyr::filter(
    season == 2024,
    season_type == "REG") %>%
  dplyr::filter(!is.na(posteam) & (rush == 1 | pass == 1))

@@

Defensive EPA per play during the 2024 NFL season is depicted as a function of offensive EPA per play in @fig-plotDefOffEPA using the `nflplotR` package [@R-nflplotR].

```{r}
#| label: fig-plotDefOffEPA
#| fig-cap: "2024 NFL Offensive and Defensive EPA Per Play."
#| fig-alt: "2024 NFL Offensive and Defensive EPA Per Play."

ggplot2::ggplot(
  data = epa_combined,
  aes(
    x = off_epa,
    y = def_epa)) +
  nflplotR::geom_mean_lines(
    aes(
      x0 = off_epa,
      y0 = def_epa)) +
  nflplotR::geom_nfl_logos(
    aes(
      team_abbr = team),
      width = 0.065,
      alpha = 0.7) +
  labs(
    x = "Offense EPA/play",
    y = "Defense EPA/play",
    title = "2024 NFL Offensive and Defensive EPA per Play"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) + # horizontal y-axis title
  scale_y_reverse()
```

>>>>

```{r}
pbp_regularSeason <- nfl_pbp %>% 
  dplyr::filter(
    season == 2025,
    season_type == "REG") %>%
  dplyr::filter(!is.na(posteam) & (rush == 1 | pass == 1))

@@

Defensive EPA per play during the 2025 NFL season is depicted as a function of offensive EPA per play in @fig-plotDefOffEPA using the `nflplotR` package [@R-nflplotR].

```{r}
#| label: fig-plotDefOffEPA
#| fig-cap: "2025 NFL Offensive and Defensive EPA Per Play."
#| fig-alt: "2025 NFL Offensive and Defensive EPA Per Play."

ggplot2::ggplot(
  data = epa_combined,
  aes(
    x = off_epa,
    y = def_epa)) +
  nflplotR::geom_mean_lines(
    aes(
      x0 = off_epa,
      y0 = def_epa)) +
  nflplotR::geom_nfl_logos(
    aes(
      team_abbr = team),
      width = 0.065,
      alpha = 0.7) +
  labs(
    x = "Offense EPA/play",
    y = "Defense EPA/play",
    title = "2025 NFL Offensive and Defensive EPA per Play"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) + # horizontal y-axis title
  scale_y_reverse()
```
